Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-01-03 SupportingInformation.Rmd
comment out extinction risk section

source("mydispersal.R")
set.seed(seed)

rlist<-c(0,0.05,0.25,0.5,0.7,0.75,0.9,1.0,1.25,1.5,1.75,1.95)

# plot for local dispersal in D matrix ; r=0 for LC model, r!=0 for Ricker model
pdf("./Results/ext_risk_local_disp.pdf",heigh=6,width=10)
op<-par(mfrow=c(3,4),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    #cat("r=",r,"\n")
    s<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=r,K=50,disp_everywhere=F,ploton=F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend(x=-0.06,y=1.1, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

# plot for global dispersal in D matrix ; r=0 for LC model, r!=0 for Ricker model
pdf("./Results/ext_risk_global_disp.pdf",heigh=6,width=10)
op<-par(mfrow=c(3,4),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
  #cat("r=",r,"\n")
  s<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=r,K=50,disp_everywhere=T,ploton=F)
  plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d_seq,s$risk_right,type="b",col="blue")
  legend(x=-0.06,y=1.1, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
  mtext(paste0("r = ", r))
}
par(op)
dev.off()

# plot to show the effect of increasing numlocs for r=0 (LC model), r=0.25 (Ricker model)
pdf("./Results/ext_risk_numlocs_effect_local_disp.pdf",heigh=6,width=6)
op<-par(mfrow=c(2,2),mar=c(4,4,1,1) + 0.1)
for(r in c(0,0.25)){
  #cat("r=",r,"\n")
  s5<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=r,K=50,disp_everywhere=F,ploton=F)
  s25<-varying_d(numsims=10000,numsteps =25,numlocs=25,r=r,K=50,disp_everywhere=F,ploton=F)

  plot(s5$d_seq,s5$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
  lines(s25$d_seq,s25$risk_left,type="b",col="orange")
  legend("topleft", title=paste0("r=",r," , left tail dep. in noise"), c("numlocs=5","numlocs=25"), fill=c('red', 'orange'),  horiz=F, bty='n')

  plot(s5$d_seq,s5$risk_right,xlim=c(0,1),ylim=c(0,1),type="b",col="blue",
       panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
  lines(s25$d_seq,s25$risk_right,type="b",col="skyblue")
  legend("topleft",title=paste0("r=",r," , right tail dep. in noise"), c("numlocs=5","numlocs=25"), fill=c('blue', 'skyblue'),  horiz=F, bty='n')
  #mtext(paste0("B",1))
}
par(op)
dev.off()

# plot to show the effect of increasing numlocs for r=0 (LC model), r=0.25 (Ricker model)
pdf("./Results/ext_risk_numlocs_effect_global_disp.pdf",heigh=6,width=6)
op<-par(mfrow=c(2,2),mar=c(4,4,1,1) + 0.1)
for(r in c(0,0.25)){
  #cat("r=",r,"\n")
  s5<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=r,K=50,disp_everywhere=T,ploton=F)
  s25<-varying_d(numsims=10000,numsteps =25,numlocs=25,r=r,K=50,disp_everywhere=T,ploton=F)

  plot(s5$d_seq,s5$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
  lines(s25$d_seq,s25$risk_left,type="b",col="orange")
  legend("topleft", title=paste0("r=",r," , left tail dep. in noise"), c("numlocs=5","numlocs=25"), fill=c('red', 'orange'),  horiz=F, bty='n')

  plot(s5$d_seq,s5$risk_right,xlim=c(0,1),ylim=c(0,1),type="b",col="blue",
       panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
  lines(s25$d_seq,s25$risk_right,type="b",col="skyblue")
  legend("topleft",title=paste0("r=",r," , right tail dep. in noise"), c("numlocs=5","numlocs=25"), fill=c('blue', 'skyblue'),  horiz=F, bty='n')
  #mtext(paste0("B",1))
}
par(op)
dev.off()

# plot to see the effect of K for r=0.25 (Ricker model)
pdf("./Results/ext_risk_K_effect.pdf",heigh=6,width=6)
op<-par(mfrow=c(2,2),mar=c(4,4,1,1) + 0.1)

s1<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=0.25,K=50,disp_everywhere=F,ploton=F)
s2<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=0.25,K=200,disp_everywhere=F,ploton=F)

s3<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=0.25,K=50,disp_everywhere=T,ploton=F)
s4<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=0.25,K=200,disp_everywhere=T,ploton=F)

plot(s1$d_seq,s1$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
lines(s2$d_seq,s2$risk_left,type="b",col="orange")
legend("topleft",title=("Noise : left tail dep., local disp."), c("K=50","K=200"), fill=c('red', 'orange'),  horiz=F, bty='n')

plot(s1$d_seq,s1$risk_right,xlim=c(0,1),ylim=c(0,1),type="b",col="blue",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
lines(s2$d_seq,s2$risk_right,type="b",col="skyblue")
legend("topleft",title=("Noise : right tail dep., local disp."),c("K=50","K=200"), fill=c('blue', 'skyblue'),  horiz=F, bty='n')

plot(s3$d_seq,s3$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
lines(s4$d_seq,s4$risk_left,type="b",col="orange")
legend("topleft",title= ("Noise : left tail dep., global disp."),c("K=50","K=200"), fill=c('red', 'orange'),  horiz=F, bty='n')

plot(s3$d_seq,s3$risk_right,xlim=c(0,1),ylim=c(0,1),type="b",col="blue",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
lines(s4$d_seq,s4$risk_right,type="b",col="skyblue")
legend("topleft",title=("Noise : right tail dep., global disp."),c("K=50","K=200"), fill=c('blue', 'skyblue'),  horiz=F, bty='n')

>>>>

#source("mydispersal.R")
#set.seed(seed)

#rlist<-c(0,0.05,0.25,0.5,0.7,0.75,0.9,1.0,1.25,1.5,1.75,1.95)

# plot for local dispersal in D matrix ; r=0 for LC model, r!=0 for Ricker model
#pdf("./Results/ext_risk_local_disp.pdf",heigh=6,width=10)
#op<-par(mfrow=c(3,4),mar=c(5,4,1,1) + 0.2)
#for(r in rlist){
    #cat("r=",r,"\n")
#    s<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=r,K=50,disp_everywhere=F,ploton=F)
#    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
#    lines(s$d_seq,s$risk_right,type="b",col="blue")
#    legend(x=-0.06,y=1.1, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
#    mtext(paste0("r = ", r))
#}
#par(op)
#dev.off()

# plot for global dispersal in D matrix ; r=0 for LC model, r!=0 for Ricker model
#pdf("./Results/ext_risk_global_disp.pdf",heigh=6,width=10)
#op<-par(mfrow=c(3,4),mar=c(5,4,1,1) + 0.2)
#for(r in rlist){
  #cat("r=",r,"\n")
#  s<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=r,K=50,disp_everywhere=T,ploton=F)
#  plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
#  lines(s$d_seq,s$risk_right,type="b",col="blue")
#  legend(x=-0.06,y=1.1, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
#  mtext(paste0("r = ", r))
#}
#par(op)
#dev.off()

# plot to show the effect of increasing numlocs for r=0 (LC model), r=0.25 (Ricker model)
#pdf("./Results/ext_risk_numlocs_effect_local_disp.pdf",heigh=6,width=6)
#op<-par(mfrow=c(2,2),mar=c(4,4,1,1) + 0.1)
#for(r in c(0,0.25)){
  #cat("r=",r,"\n")
#  s5<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=r,K=50,disp_everywhere=F,ploton=F)
#  s25<-varying_d(numsims=10000,numsteps =25,numlocs=25,r=r,K=50,disp_everywhere=F,ploton=F)

#  plot(s5$d_seq,s5$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
#  lines(s25$d_seq,s25$risk_left,type="b",col="orange")
#  legend("topleft", title=paste0("r=",r," , left tail dep. in noise"), c("numlocs=5","numlocs=25"), fill=c('red', 'orange'),  horiz=F, bty='n')

#  plot(s5$d_seq,s5$risk_right,xlim=c(0,1),ylim=c(0,1),type="b",col="blue",
#       panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
#  lines(s25$d_seq,s25$risk_right,type="b",col="skyblue")
#  legend("topleft",title=paste0("r=",r," , right tail dep. in noise"), c("numlocs=5","numlocs=25"), fill=c('blue', 'skyblue'),  horiz=F, bty='n')
  #mtext(paste0("B",1))
#}
#par(op)
#dev.off()

# plot to show the effect of increasing numlocs for r=0 (LC model), r=0.25 (Ricker model)
#pdf("./Results/ext_risk_numlocs_effect_global_disp.pdf",heigh=6,width=6)
#op<-par(mfrow=c(2,2),mar=c(4,4,1,1) + 0.1)
#for(r in c(0,0.25)){
  #cat("r=",r,"\n")
#  s5<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=r,K=50,disp_everywhere=T,ploton=F)
#  s25<-varying_d(numsims=10000,numsteps =25,numlocs=25,r=r,K=50,disp_everywhere=T,ploton=F)

#  plot(s5$d_seq,s5$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
#  lines(s25$d_seq,s25$risk_left,type="b",col="orange")
#  legend("topleft", title=paste0("r=",r," , left tail dep. in noise"), c("numlocs=5","numlocs=25"), fill=c('red', 'orange'),  horiz=F, bty='n')

#  plot(s5$d_seq,s5$risk_right,xlim=c(0,1),ylim=c(0,1),type="b",col="blue",
#       panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
#  lines(s25$d_seq,s25$risk_right,type="b",col="skyblue")
#  legend("topleft",title=paste0("r=",r," , right tail dep. in noise"), c("numlocs=5","numlocs=25"), fill=c('blue', 'skyblue'),  horiz=F, bty='n')
  #mtext(paste0("B",1))
#}
#par(op)
#dev.off()

# plot to see the effect of K for r=0.25 (Ricker model)
#pdf("./Results/ext_risk_K_effect.pdf",heigh=6,width=6)
#op<-par(mfrow=c(2,2),mar=c(4,4,1,1) + 0.1)

#s1<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=0.25,K=50,disp_everywhere=F,ploton=F)
#s2<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=0.25,K=200,disp_everywhere=F,ploton=F)

#s3<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=0.25,K=50,disp_everywhere=T,ploton=F)
#s4<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=0.25,K=200,disp_everywhere=T,ploton=F)

#plot(s1$d_seq,s1$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
#lines(s2$d_seq,s2$risk_left,type="b",col="orange")
#legend("topleft",title=("Noise : left tail dep., local disp."), c("K=50","K=200"), fill=c('red', 'orange'),  horiz=F, bty='n')

#plot(s1$d_seq,s1$risk_right,xlim=c(0,1),ylim=c(0,1),type="b",col="blue",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
#lines(s2$d_seq,s2$risk_right,type="b",col="skyblue")
#legend("topleft",title=("Noise : right tail dep., local disp."),c("K=50","K=200"), fill=c('blue', 'skyblue'),  horiz=F, bty='n')

#plot(s3$d_seq,s3$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
#lines(s4$d_seq,s4$risk_left,type="b",col="orange")
#legend("topleft",title= ("Noise : left tail dep., global disp."),c("K=50","K=200"), fill=c('red', 'orange'),  horiz=F, bty='n')

#plot(s3$d_seq,s3$risk_right,xlim=c(0,1),ylim=c(0,1),type="b",col="blue",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
#lines(s4$d_seq,s4$risk_right,type="b",col="skyblue")
#legend("topleft",title=("Noise : right tail dep., global disp."),c("K=50","K=200"), fill=c('blue', 'skyblue'),  horiz=F, bty='n')

#par(op)
#dev.off()
```
